Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-09-20 article/sections/numerical_implementation.tex
added preliminary text/motication to multipole filtering section and some points to the discussions

Motivated by these observations we also compute the Stokes Q \& U maps corresponding to B-modes of polarization by simply subtracting the Stokes Q \& U maps corresponding to E-mode from the total Stoker Q \& U maps. For completeness we also compute the Stokes Q \& U maps corresponding to E-mode in an analogous manner. We carry out a spectral study on these Stokes Q \& U maps corresponding to E \& B modes, computed using this alternate method. The results of the spectral analysis are summarized in \fig{fig:dbqu-spectra_rad_cutoff}.
%
\begin{figure}[!t] 
\centering
%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dequ-spectra-radial-cutoff.pdf}}
%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dbqu-spectra-radial-cutoff.pdf}} \\[-5ex]
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-equ-de-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-db-spectrum-radial-cutoff.pdf}}
\caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}. The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\equ=\fqu-\fqu_{Local}^B$, $\bqu=\fqu-\fqu_{Local}^{E}$.}
\label{fig:dbqu-spectra_rad_cutoff}
\end{figure}
%
We observe that the the low multipole spectral behavior is not affected by this alternate construction of pure Stokes Q \& U maps. The high multipole behavior is significantly altered as can be seen by comparing \fig{fig:dbqu-spectra_rad_cutoff} with lower panels of \fig{fig:equ-bqu-spectra_rad_cutoff}. The relative percentage difference with respect to the reference spectra is seen to lie well within 2\% error for sufficiently high multipoles for all radial cutoff $r_{\rm cutoff}$.
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Multipole filtering using spatial convolutions}
%--------------------------------------------------------
%--------------------------------------------------------

>>>>

Motivated by these observations we also compute the Stokes Q \& U maps corresponding to B-modes of polarization by simply subtracting the Stokes Q \& U maps corresponding to E-mode from the total Stoker Q \& U maps. For completeness we also compute the Stokes Q \& U maps corresponding to E-mode in an analogous manner. We carry out a spectral study on these Stokes Q \& U maps corresponding to E \& B modes, computed using this alternate method. The results of the spectral analysis are summarized in \fig{fig:dbqu-spectra_rad_cutoff}.
%
\begin{figure}[!t] 
\centering
%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dequ-spectra-radial-cutoff.pdf}}
%\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/dbqu-spectra-radial-cutoff.pdf}} \\[-5ex]
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-equ-de-spectrum-radial-cutoff.pdf}}
\subfigure[]{\includegraphics[width=0.49\columnwidth]{simulated/qu2equbqu/relative-percentage-err-bqu-db-spectrum-radial-cutoff.pdf}}
\caption{This figure depicts the same as the bottom panel of \fig{fig:equ-bqu-spectra_rad_cutoff}. The Stokes Q and U maps corresponding to E and B modes used in this analysis are constructed using the following relations: $\fqu_{E}=\fqu-\fqu_{Local}^B$, $\fqu_{B}=\fqu-\fqu_{Local}^{E}$.}
\label{fig:dbqu-spectra_rad_cutoff}
\end{figure}
%
We observe that the the low multipole spectral behavior is not affected by this alternate construction of pure Stokes Q \& U maps. The high multipole behavior is significantly altered as can be seen by comparing \fig{fig:dbqu-spectra_rad_cutoff} with lower panels of \fig{fig:equ-bqu-spectra_rad_cutoff}. The relative percentage difference with respect to the reference spectra is seen to lie well within 2\% error for sufficiently high multipoles for all radial cutoff $r_{\rm cutoff}$.
%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Multipole filtering using spatial convolutions}
As we have seen in the previous section that recovering large scale modes using local convolutions is not possible. The small angular scales however are reliably recovered. However the local convolution methods can be used to recover competent spectra. 
Many CMB experiments cannot access the large angle modes due to limited sky coverage. Often the large angle analysis is deal with in pixel space owing to the non-Gaussianity of the likelihood functions. With all these as motivations we study how the radial filters are modified by removing the large scale modes. We try to understand how removing large scale modes effects the locality of the E and B map estimators. We demonstrate that it is possible to get filtered maps by using the modifying the radial filter. 
%--------------------------------------------------------
%--------------------------------------------------------
